\section{Basics}

\begin{mydef}
Given a Field $k$, the $\emph{Projective Space of Degree n over k}$, denoted $\mathbb{P}^n_k$
is the quotient $(k^{n+1} \setminus \{\bold{0}\}) / \sim$, where $\sim$ is the equivalence relation 
defined as 
\[
(x_0, ..., x_n) \sim (y_0, ..., y_n)~if~\exists \lambda \in k~s.t.~\lambda \neq 0,
(x_0, ..., x_n) = (\lambda y_0, ..., \lambda y_n)
\]
Given this, points in projective space are often denoted $P = [ x_0 : ... : x_n]$,
with the colons and brackets indicating this is an equivalence class. So then,
$[ y_0: ... : y_n ] = P = [ x_0 : ... : x_n ]$ if $(y_0, ..., y_n) \sim (x_0, ..., x_n)$.
\end{mydef}
The definition is abstract to purposely highlight the fact that, 
given a field $k$ we can create a projective space.
Effectively, the projective space is the set of all lines in 
$k^n$ through the origin. This is also why the projective space
has one fewer dimension than its corresponding vector space.

So, the ``points" in projective space are lines in the corresponding
vector space. Another interesting feature of projective space is
that parallel lines intersect at a ``point at infinity". This can
be thought of as making partitions of lines in the projective space
pased on parallelism, as if we were defining an equivalence relation.
Now, each equivalence class is assigned a unique ``point at infinity"
that each line in the equivalence class intersects. Thus, if two lines
are parallel, they intersect at some point at infinity. Likewise, if
two lines aren't parallel, they'll have their own points at infinity,
but they won't be the same, thus they will only have the usual intersection
normally expected of non-parallel lines.

This may seem very strange, but can be illustrated with a stereographic
projection. Suppose we're in $\mathbb{R}^3$, and picture two things:
the plane $z=1$ and a sphere of radius 1 centered at the origin.
Now, we can map any point $p$ on $z=1$ to a unique point on the upper
hemisphere of our sphere; simply note that the line passing through
$p$ and the origin $(0, 0, 0)$ intersects the specified hemisphere
precisely once at some point $q$. Knowing this, we can see that lines
on our plane $z=1$ are mapped to great circles on our sphere. In the
case of two parallel lines, they will never intersect in $z=1$, but
the great circles they're mapped to will intersect on the equator of 
the hemisphere.

\begin{mydef}
A function $f(x)$ is \emph{Homogenous of Degree n} if, for some 
constant $\lambda$, we have $f(\lambda x) = \lambda ^n f(x)$.
If $f$ is a homogenous polynomial of degree n, it is known as a \emph{form of degree n}.
\end{mydef}

Homogenous functions are particularly useful when considering their
sets of zeroes in projective space. If $f$ is homogenous of degree
n, and some point $x = (x_0, ..., x_n)$ is a zero of $f$, then
$f(\lambda x) = \lambda^n f(x) = \lambda^n 0 = 0$. Thus, we can say
that, if $f$ is homogenous, then we can indeed have zeroes of $f$ in $\mathbb{P}^n_k$,
assuming k is algebraically closed.

\begin{mydef}
\[
S_d = \{\text{ forms of degree d in $(X, Y, Z)$}\}
\]
So, any element $F$ of $S_d$ can be written in a unique way as:
\[
F = \Sigma _{\substack{i+j+k'=d \\ i,j,k' > 0}}~a_{i,j,k'} X^i Y^j Z^{k'},~a_{i,j,k'} \in k
\]
\end{mydef}
So, $S_d$ has a basis of 
%improve formatting later...
\begin{align*}
\{&X^d, X^{d-1}Y, X^{d-2}Y^2, \dots\\
&X^{d-1}Z, X^{d-2}YZ, X^{d-3}Y^2Z, \dots\\
&X^{d-2}Z^2, X^{d-3}YZ^2, X^{d-4}Y^2Z^2, \dots\\
\vdots\\
&\}
\end{align*}
Also, it can be seen that $\dim S_d = {d+2 \choose 2}$. On its own
$S_d$ isn't incredibly interesting, but we can make use of it when
reasoning about certain sets of geometric objects.

\begin{mydef}
for $p_1, \dots, p_n \in \mathbb{P}^2$, let
\[
	S_d(p_1, \dots, p_n) = \{ F \in S_d :~F(p_i) = 0,~i=1,\dots,n\}
\]
\end{mydef}

\begin{mydef}
A \emph{line} in $\mathbb{P}^2$ is defined as the points for which
some linear form $aX + bY + cZ$ is zero. This is notated
\[
L:(aX+bY+cZ=0)
\]
\end{mydef}

\begin{mydef}
A \emph{Conic} in $\mathbb{R}^2$ is a plane curve given by the quadratic
equation
\[
q(x,y) = ax^2 + bxy + cy^2 + dx + ey + f = 0
\]
\end{mydef}

To ``adapt" this definition into projective space $\mathbb{P}^2$, we simply
note that the inhomogenous polynomial $q$ has an associated
homogenous polynomial 
\[
Q(X,Y,Z) = aX^2 + bXY + cY^2 + dXZ + eYZ + fZ^2
\]
Miles Reid recommends thinking about this as a bijection $q \leftrightarrow Q$ by
\[
q(x,y) = Q(\frac{X}{Z},\frac{Y}{Z},\frac{Z}{Z}),~Z\ne 0
\]
Thus, a conic in $\mathbb{P}^2$ would be determined by the zeroes of $Q$.

\begin{mydef}
A \emph{Projective Transformation} on $\mathbb{P}^2_\mathbb{R}$ is a
transformation of the form
\[
T(x) = Mx
\]
where $x$ is some point in $\mathbb{P}^2_\mathbb{R}$ in homogenous coordinates in vector form,
and $M$ is a non-singular $3\times3$ matrix.
\end{mydef}

More explicitly, if we restrict ourselves to $\mathbb{R}^2 \subset \mathbb{P}^2_\mathbb{R}$
(eg: the $Z=1$ plane) then we can think of this as
\[
\begin{bmatrix}
x\\
y
\end{bmatrix} \mapsto
(A\begin{bmatrix}
x\\
y
\end{bmatrix} + B) / (cx+dy+e)
\]
when $cx+dy+e \ne 0$. Thus, we can define the matrix $M$ as follows:
\[
M= \left[\begin{array}{cc|c}
\multicolumn{2}{c|}{A} & B\\
\hline
c & d & e
\end{array}\right]
\]

Interestingly, this is a somewhat subtle way of demonstrating that certain
non-linear transformations (projective and affine translation) in $n$
dimensions can actually be achieved using linear transformations in $n+1$ dimensions.

\begin{theorem}
Let $k$ be any field of characteristic $\ne 2$. Then, any quadratic form $Q$
in $(X,Y,Z)$ has an associated $3 \times 3$ symmetric matrix $A$ s.t.
\[
x^TAx =  Q(X,Y,Z),~x=\begin{bmatrix}
x\\
y\\
z
\end{bmatrix}
\]
explicitly, if 
\[
Q(X,Y,Z) = aX^2 + 2bXY + cY^2 + 2dXZ + 2eYZ + fZ^2
\]
Then
\[
A = \begin{bmatrix}
a & b & d\\
b & c & e\\
d & e & f
\end{bmatrix}
\]
and the quadratic form (and hence the conic it defines) is non-degenerate
if the matrix $A$ is non-degenerate (non-singular).
\end{theorem}

Note that the matrix $A$ from the above theorem is symmetric. Thus, we can
apply the Spectral Theorem to see that we can diagonalize it using some
orthogonal matrix. This effectively allows us to transform any non-degenerate 
quadratic form into a homogenous quadratic form through a change of basis.

\begin{theorem}
Let $Q$ be a quadratic form of $X, Y, Z$. Then, there exists a change of basis $(X,Y,Z) \mapsto (X',Y',Z')$ s.t.
$Q(X,Y,Z) = Q'(X',Y',Z')$ where
\[
Q'(X',Y',Z') = \lambda_1 X'^2 + \lambda_2 Y'^2 + \lambda_3 Z'^2
\]
As a corollary, all non-degenerate conics in $\mathbb{P}^2$ are projectively
equivalent to the conic defined by $XZ = Y^2$. That is, there is some
projective transformation which takes an arbitrary conic $C$ to the conic 
defined by $XZ = Y^2$.
\end{theorem}
\begin{proof}
$Q$ is a quadratic form,
thus $Q$ has an associated symmetric matrix 
$A$ s.t. $Q(x) = x^TAx$. As $A$ is symmetric, the Spectral Theorem gives that
\[
\exists P:~P\text{ orthogonal},~P^TAP\text{ is diagonal}
\]
and in fact, the diagonal entries of $B=P^TAP$ are the eigenvalues of $A$. Thus,
it is easy to show, using the transformation $x=Px'$, that
\[
Q(X,Y,Z) = x^TAx = (Px')^TAPx' = x'^TP^TAPx' = x'^TBx'
\]
Now, letting the eigenvalues of $A$ be $\lambda_1, \lambda_2, \lambda_3$ we see that
\[
x'^TBx' = \lambda_1 X'^2 + \lambda_2 Y'^2 + \lambda_3 Z'^2 = Q'(X',Y',Z')
\]
Thus, $Q(X,Y,Z) = Q'(X',Y',Z')$.
\end{proof}
