\section{Bezout's Theorem}
Bezout's theorem will be important later, but we
probably won't be able to fully prove it here. However,
the book does prove the limited cases that we'll most rely on.

\begin{theorem}
\emph{Homogenous Forms in 2 Variables}:\\

Let $F(U,V)$ be a non-zero homogenous polynomial of degree $d$ in $U,V$,
with coefficients from a fixed field $k$. Then, we call $F$ a \emph{form of degree d},
and can see that
\[
F(U,V) = a_dU^d+a_{d-1}U^{d-1}V + \dots + a_iU^iV^{d-i}+\dots+a_0V^d
\]
Now, if we apply $u=U/V$ and hold $V=1$ we have an associated non-homogenous polynomial
\[
f(u) = a_du^d + a_{d-1}u^{d-1} + \dots + a_iu^i + \dots + a_0
\]
And so, for some $\alpha \in k$
\[ %a for k-valued root, alpha for... something in P^1?
f(a) = 0 \iff (u-a)|f(u) \iff (U-\alpha V) | F(U,V)
\]
As $f$ must contain at least a linear term whose root is $a$, and
thus applying $u=U/V$, we get $(U/V - a) = (U - \alpha V)$. Now, 
holding $V=1$ like earlier, we see that
\[
(U-\alpha V) | F(U,V) \iff F(\alpha,1) = 1
\]
So, zeroes of the simpler polynomial $f$ correspond to zeroes of $F$
on $\mathbb{P}^1_k$ so long as $V \ne 0$. However, if $F$ had a root
of the form $(\beta,0)$ then certainly by homogeneity $F$ also has
$(1,0)$ as a root, giving:
\[
F(1,0) = 0 \iff a_d \cdot 1 + a_{d-1} \cdot 1 \cdot 0 + \dots + a_0 \cdot 0 = 0 \iff a_d = 0
\]
which would force $deg f < d$, as then the highest power of $U$ in $F$ is strictly
less than $d$. In this situation, $(1,0)$ is effectively a ``root at $\infty$" in $\mathbb{P}^1_k$.

Now, we can define the \emph{multiplicity} of a zero of $F$ as:
\begin{align*}
&\text{The multiplicity of $f$ at the corresponding $a \in k$}\\
&\text{$d - deg f$ if $(1,0)$ is the zero}
\end{align*}

\end{theorem}

\begin{theorem}
\emph{Bezout's Theorem}:\\

If $C$ and $D$ are plane curves of degree $m$ and $n$ (respectively)
then $C \cap D$ contains precisely $mn$ points, provided:
\begin{align*}
&\text{The field we're working over is algebraically closed} \tag{i}\\
&\text{Points of intersection are counted with multiplicity} \tag{ii}\\
&\text{We work in $\mathbb{P}^2_k$ to account for points at infinity} \tag{iii}\\
\end{align*}
\end{theorem}

Instead of proving the general theorem, we'll only cover a special 
case of particular importance to us; intersections involving
lines and conics.

\begin{theorem}
Let $L \subset \mathbb{P}^2_k$ be a line (respectively, $C \subset \mathbb{P}^2_K$ a non-degenerate conic)
and $D \subset \mathbb{P}^2_k$ a curve defined by $D:(G_d(X,Y,Z)=0)$ where $G$ is
a form of degree $d$ in the 3 variables $X,Y,Z$. Also, assume that $L \not\subset D$ (resp. $C \not\subset D$).
Then
\[
|L \cap D| \le d
\]
and respectively
\[
|C \cap D| \le 2d
\]
And in fact, once accounting for multiplicity, points at infinity, and if $k$ is algebraically
closed, we have equality.
\end{theorem}

\begin{proof}
The line $L$ is defined as the set of zeroes of some linear form $\lambda$; $L:(\lambda=0)$
in $X,Y,Z$. Well, as a line we can certainly paramaterize $L$ using 
\[
X=a(U,V),~Y=b(U,V),~Z=c(U,V)
\]
where $a, b, c$ are linear forms of $U,V$. As an example, if $\lambda = \alpha X + \beta Y + \gamma Z$
with $\gamma \ne 0$ then we could paramaterize $L$ as
\[
X = U,~Y=V,~Z=-\frac{\alpha}{\gamma}U - \frac{\beta}{\gamma}V
\]
by simply noting that $\lambda = 0 \implies 0 = \alpha X + \beta Y + \gamma Z$ and solving
for $Z$. If $\gamma = 0$ we have the simpler case of $0 = \alpha X + \beta Y$.
Similarly, a non-degenerate conic can be parameterized as follows
\[
X=a(U,V),~Y=b(U,V),~Z=c(U,V)
\]
where $a,b,c$ are quadratic forms in $U,V$. This is because $C$ is a projective
transformation of $XZ=Y^2$, which is parametrically $(X,Y,Z) = (U^2,UV,V^2)$.
Thus, $C$ is given by 
\[
\begin{bmatrix}
X\\
Y\\
Z
\end{bmatrix}
=
M
\begin{bmatrix}
U^2\\
UV\\
V^2
\end{bmatrix}
\]
Where $M$ is a non-singular 3x3 matrix. (JUSTIFY THIS!!!)

So, in order to find the points of intersection of $L$ (resp. $C$) with $D$,
we simply need to evaluate $G_d|_L=0$ (resp. $G_d|_C=0$) using the above parameterizations.
Explicitly, to find the points of $L \cap D$ we want to find the solutions to
\[
	G_d(a(U,V),b(U,V),c(U,V)) = 0
\]
Now we can see that, as $G_d$ is a form of degree $d$ in $X,Y,Z$, and $a,b,c$ are forms
of degree 1 (resp. 2) in $U,V$ then $G_d|_L$ is of degree $d$ (resp. 2d) in $U,V$.
\end{proof}
