\documentclass[draft]{article}
\usepackage{amssymb,amsmath,amsthm,amsfonts}
\renewcommand{\abstractname}{Introduction} %change title of the abstract section
\newtheorem{mydef}{Definition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}{Theorem}[section]

\begin{document}


\title{Algebraic Geometry}
\author{Zandi} %will use full information for assignment submission
\date{\today}
\maketitle

%TODO: remove me when finished
THIS IS A DRAFT. Expect inaccuracte and incomplete information.

\begin{abstract}
Algebraic Geometry is a field of mathematics with roots as far back as
at least the 19\textsuperscript{th} century, and with major advancement and applications
in recent years. At its core, Algebraic Geometry is concerned with 
studying the sets of zeroes of a system of polynomials, in particular 
their algebraic structure. Though real polynomials are surely the first
that come to mind, much of the power in Algebraic Geometry comes from the
generalization to polynomials with coefficients in arbitrary fields.\\

The undergraduate mathematics student would hopefully find this paper accessible,
but experience with algebra and geometry would help. A ``Basics" section is included,
but will not be exhaustive. As unhelpful as it seems, it's recommended to 
do independent research as necessary using Wikipedia, YouTube (videotaped lectures)
and the referenced textbooks.

This paper draws heavily from ``Undergraduate Algebraic Geometry" by Miles Reid, 
with the primary addition being annotated proofs. Where Reid's proofs
left details to the reader, these details are mostly provided, although
the proofs remain the same.
\end{abstract}

%\input{basics.tex}
\include{basics}
\include{conic-sections}
\include{bezouts-theorem}
\include{elliptic-curves}

\end{document}
